An IFS study of Low-powered Radio Galaxies

### 2018-01-15 paper.tex
EoDC:
Integrated MNRAS template

Work on stellar kinematics section

 On branch master
 Changes to be committed:
	new file:   M_k_binned.png
	new file:   lambda_R_ellipticity.png
	modified:   paper.tex

%\documentclass[a4paper,11pt]{article}
\documentclass[fleqn,usenatbib,useAMS]{mnras}
\usepackage{amssymb}
\usepackage{natbib} % references in text to look like MNRAS/ApJ/A&A
% \usepackage{hyperref} % references become hyperlinks to bibliography
% \hypersetup{
% 	colorlinks,
% 	citecolor=black,
% 	filecolor=black,
% 	linkcolor=black,
% 	urlcolor=black
% }
\usepackage{amsmath} % align enviroment 
% \usepackage{gensymb} % degree symbol in math enviroments
\usepackage{mhchem} % typeset chemistry symbols
% \usepackage{ccaption} % for contcaption to continue figure onto multiple pages
\usepackage[flushleft, referable]{threeparttablex} % Adding notes under tables
\usepackage{multirow} % for multirow command
\usepackage{url}
\urlstyle{same}

\usepackage{array} % For wrapping text in cell in tables
% \newcolumntype{C}[1]{>{\centering\arraybackslash}p{#1}} % centered wrapped text in tables
\newcolumntype{L}[1]{>{\raggedright\let\newline\\\arraybackslash\hspace{0pt}}m{#1}} % 
\newcommand{\bracket}[1]{[#1]} % to be able to use [] in arguments

\defcitealias{Thomas2010}{TMJ} % TMJ alias

\title{An IFS study of Low-powered Radio Galaxies}
\author[J. Warren et al.]{
Joshua Warren,$^{1}$\thanks{Contact e-mail: \href{mailto:joshua.warren@physics.ox.ac.uk}{joshua.warren@physics.ox.ac.uk}}
Martin Bureau,$^{1}$
Bernd Hasemann,$^{2}$
Isabella Prandoni,$^{3}$ \newauthor
Francesco Santoro,$^{3}$
Robert Laing,$^{3}$
Paola Parma,$^{3}$
Hans de Ruiter$^{3}$
and Arturo Mignano$^{3}$
\\
$^{1}$Sub-department of Astrophysics, Department of Physics, University of Oxford, Denys Wilkinson Building, Keble Road, Oxford OX1 3RH, UK\\
$^{2}$European Southern Observatory, Karl-Schwarzschild-Str. 2, 85748 Garching b. München, Germany\\
$^{3}$INAF - Istituto di Radioastronomia, Via P. Gobetti 101, 40129 Bologna, Italy}

\begin{document}
\maketitle

%\date{Oxford, \today} % date is given automatically at top of page in mnras formatting

\begin{abstract}

\end{abstract}

@@

	% One identifier of AGNs is a radio signature consistent with Synchrotron emission from the outflow i.e a radio galaxy (RG). These are typically categorized into one of two classes: Fanaroff-Riley (FR) I or FR II \citep{Fanaroff1974}. Of these we focus on the former since these are by far the most common mode in the local universe (possibly as far as $z \sim 1$ \citep{Rigby2008}), and so to discuss radio AGN feedback is to consider feedback from FR I sources \citep{DeYoung2010}. Indeed, while there is broad consensus \citep{Heckman1986, Baum1992} that the brightest RGs (mostly FR IIs) are caused when a massive galaxy merges with a gas rich galaxy (a wet merger) giving a plentiful fuel reservoir to the AGN \citep{Baum1992}, there is much more debate when it comes to low-powered ($P_\mathrm{1.4 GHz} \lesssim 10^{24.5} \, \mathrm{W Hz^{-1}}$) RGs (mostly FR I). Suggestions fall into two categories: an extrapolation of radio-loud galaxies (i.e. a merger with either small gas reservoirs or low efficiency accretion onto the SMBH) or a highly efficient accretion of gas from secular origins (such as Bondi accretion of the hot X-ray component of the Inter-Stellar Medium (ISM) \citep{Allen2006} or from existing cold gas reservoirs \citep{Prandoni2010}). This project aims to add to this discussion using Integral Field Unit (IFU) observations in the visible band of nearby radio galaxies and comparing this with Atlas-3D sample \citep{Cappellari2011} as a control sample.

@@

@@

	\begin{table*}
		\centering
	\begin{threeparttable}
		\caption{Key sample characteristics of the Southern Sample galaxies.}
		\label{tab:sample}
		\begin{tabular}{l c c c c l}
			\hline
			\hline
			Host galaxy	& Radio source 	& Redshift	& $S_\text{1.4\,GHz}$	& $m_K$ & Dust morphology\\
						& (PKS) 		& 			& (mJy) 			& (mag)	&\\
			\hline 
			ESO 443-G024 & 1258-321 	& 0.01703	& $1387 \pm 45$		& 8.51 & no dust\tnote{a}	\\ 
			IC 1459 	& 2254-367 		& 0.00565 	& $1280 \pm 45$		& 6.81 & dust lane\tnote{b}	\\
			IC 1531 	& 0007-325 		& 0.02553 	& \leavevmode\phantom{0}$388 \pm 12$		& 9.55 & --					\\
			IC 4296		& 1333-\leavevmode\phantom{0}33 		& 0.01248 	& $1342 \pm 41$		& 7.50 & edge-on disc\tnote{b} \\
			NGC 612 	& 0131-\leavevmode\phantom{0}36 		& 0.02954 	& \leavevmode\phantom{0}$585 \pm 18$		& 9.58 & dust lane\tnote{c}	\\
			NGC 1316 	& 0320-\leavevmode\phantom{0}37 & 0.00591 	& \leavevmode\phantom{0}$255 \pm 10$		& 5.59 & dust patches\tnote{b} \\
			NGC 1399 	& 0336-\leavevmode\phantom{0}35 & 0.00472 	& \leavevmode\phantom{0}$209 \pm \leavevmode\phantom{0}7$	& 6.31 & no dust\tnote{b}	\\
			NGC 3100 	& 0958-314 		& 0.00879 	& \leavevmode\phantom{0}$530 \pm 16$		& 8.08 & dust lane\tnote{d}	\\
			NGC 3557 	& 1107-372 		& 0.01016 	& \leavevmode\phantom{0}$484 \pm 16$		& 7.20 & face-on disc\tnote{b}\\
			NGC 7075 	& 2128-388 		& 0.01819 	& \leavevmode\phantom{0}$837 \pm 28$		& 9.56 & --					\\
			--			& 0718-\leavevmode\phantom{0}34 		& 0.02897 	& $1119 \pm 41$		& 9.97 & dust patches\tnote{e} \\
			\hline
			\hline
		\end{tabular}
		\begin{tablenotes}
		\footnotesize
		\note Col.\,1: host galaxy name. Col.\,2: radio source name from Parkes Southern Radio Source Catalogue. Col.\,3: redshift. Col.\,4: National Radio Astronomy Observatory (NRAO) Very Large Array (VLA) Sky Survey (NVSS) 1.4 GHz flux density \citep{Condon1998}. Col.\,5: Two Micron All Sky Survey (2MASS) $K$-band apparent magnitude (with errors of $\pm 0.025$ mag; \citealt{Skrutskie2006}). Col.\,6: dust morphologies from (a) \citet{Govoni2000}, (b) \citet{Lauer2005}, (c) \citet{Bettoni2001}, (d) \citet{Sandage1979}, (e) \citet{Colbert2001}. 
		\item We hereafter refer to the last galaxy by its PKS name only.
		\end{tablenotes}
	\end{threeparttable}
	\end{table*}

@@

	Following this, we noted that the cubes where still not properly calibrated. Three main issues remain: the quadrants have different intensities, clearly showing uncorrected throughput differences; diagonal intensity stripes are present in the reconstructed images at all wavelengths; and spectral features are observed \citep{Jullo2008} that are visually similar to fringe patterns caused by interference within the CCD between incident light and light reflected from the interfaces between layers of the CCD materials. \citet{Lagerholm2012} present ad-hoc methods to correct for these issues, which we here adopt. These additional steps mean that the datacubes are not perfectly flux-calibrated, but all the corrections are multiplicative and thus will not effect equivalent width or line ratio measurements. From comparisons to the MUSE data (see Section \ref{sec:MUSE}), we then estimate the flux calibration of the resulting datacubes.

@@

		Finally, we trimmed all the MUSE cubes to the central $30\arcsec \times 30\arcsec$ ($150 \times 150$\,spaxels) only, to (a) avoid the regions used for the pseudo-sky spectrum and (b) reduce the computing resources required for spatial binning (see Section \ref{sec:analysis}). In any case, the bins would be so large in the outer parts as to be effectively useless (see Fig\,\ref{fig:egSNR}).

\section{Data Analysis}
	\label{sec:analysis}
	From this point on, the VIMOS and MUSE datasets are treated almost identically, the only difference (other than the different spectral ranges and resolutions) being that the MUSE datacubes are spatially binned to a higher signal-to-noise ratio (S/N) using Voronoi binning\footnote{\url{http://www-astro.physics.ox.ac.uk/~mxc/software/}} \citep{Cappellari2003}. For our purposes, we define the `signal' and `noise' of each spaxel as the median value of its spectrum and noise spectrum, respectively. We require a S/N of 30 for all VIMOS datacubes and 50 for the IC 1459 and IC 4296 MUSE datacubes. The NGC 1316 and NGC 1399 MUSE datacubes were binned to a S/N of 50 for the analysis of the stellar kinematics and 100 for the analysis of the emission line kinematics and stellar populations.

	Next we implement a routine to find optimal initial guesses of the redshift and velocity dispersion for each galaxy, to be used when fitting individual bins, by means of iterative fits to the spatially collapsed (i.e. summed across both spatial dimensions of the datacube) spectrum. We use the penalized-fitting (\textsc{pPXF}) routine\footnote{\url{http://www-astro.physics.ox.ac.uk/~mxc/software/}} of \citet{Cappellari2004} and \citet{Cappellari2016a} with the Medium-resolution Issac Newton Telescope (INT) Library of Empirical Spectra (MILES) library \citep{Sanchez-Blazquez2006, Falcon-Barroso2011a} to find the best-fitting line-of-sight velocity distribution (LOSVD; as parametrised by the Gaussian parameters $v$, the mean velocity and $\sigma$, the velocity dispersion). The final mean velocity of a given galaxy, is used as its precise spectroscopic redshift and is given in Table \ref{tab:sample}. Beyond this point, each bin is analysed independently.

@@

		\begin{table}
	 		\centering
	 	\begin{threeparttable}
	 		\caption{Emission lines considered in the \textsc{pPXF} fits.}
	 		\label{tab:EmissionLine}
	 		\begin{tabular}{l c c c}
	 		\hline
	 		\hline
	 		Emission & Rest-frame & Doublet rest-frame & Amplitude  \\
	 		Line & wavelength & wavelength & ratio \\
	 		 & (\AA) & (\AA) \\
	 		\hline
	 		\bracket{\ion{O}{ii}} 	& 3726.03 & 3728.82 & Free \\
	 		H\,$\delta$ 	& 4101.76 & -- & -- \\
	 		H\,$\gamma$ 	& 4340.47 & -- & -- \\
	 		H\,$\beta$ 		& 4861.33 & -- & -- \\
	 		\bracket{\ion{O}{iii}}	& 4958.92 & 5006.84 & 0.35 \\
	 		\bracket{\ion{N}{i}} 	& 5199.36 & 5201.86 & 0.65 \\
	 		\bracket{\ion{O}{i}} 	& 6300.30 & 6363.67 & 0.33 \\
	 		\bracket{\ion{N}{ii}} 	& 6548.03 & 6583.41 & 0.34 \\
	 		H\,$\alpha$ 	& 6562.30 & -- & -- \\
	 		\bracket{\ion{S}{ii}} 	& 6716.47 & 6730.85 & Free \\
	 		\hline
	 		\hline
	 		\end{tabular}
	 		\begin{tablenotes}
	 		\note Col\,1: Emission line name. Col\,2: Emission line rest-frame wavelength. Col\,3: Doublet rest-frame wavelength for forbidden lines. Col\,4: The fixed ratio of the amplitudes of the lines within a doublet. `Free' indicates the amplitudes of both doublet constituents are fit independently of each other. 
	 		\end{tablenotes}
	 	\end{threeparttable}
	 	\end{table}

@@

		\subsubection{Correcting for Stellar Velocity Dispersion}
			We correct for the effect of the different velocity dispersions of the stars which varyingly spread absorption features such that differing fractions of the absorption is outside of the central bandpasses. To do this, we create a best-fitting spectrum (as in the previous step) which is \textit{not} convolved with the best-fitting LOSVD. A given index, $I$, is then measured for both this `unconvolved' spectrum ($I^\text{unc}$) and the convolved best-fitting spectrum ($I^\text{conv}$), and the ratio of these two indices is used as a multiplicative correction factor for the index measured ($I^\text{obs}$), such that the corrected index ($I^\text{corr}$) is given by
			\begin{equation}
				I^\text{corr} \equiv \frac{I^\text{unc}}{I^\text{conv}} I^\text{obs} \, .
			\end{equation}
			These corrected indices are those reported and discussed in the sections below.

@@

\section{Stellar Kinematics}
	\label{sec:StarKine}
	Using the methods above, we produce stellar kinematic maps for all datacubes (shown in Section \ref{sec:Maps}). Here we use these maps to classify each galaxy according to the Atlas$^\text{3D}$ regular/non-regular rotator and fast/slow rotator classification schemes of \citet{Krajnovic2006} and \citet{Cappellari2016}, respectively, as well as the qualitative kinematic classes of \citet{Krajnovic2011}.

	% Ellipticity is measured as the ellipticity of the best-fitting ellipse to the surface-brightness map with an mean radius $R_\mathrm{m}$, of 1 effective radius $R_\mathrm{e}$. Firstly the centre of the galaxy is found as the luminosity weighted centre using the \textsc{python} routine \textsc{find\_galaxy}, which is part of the \textsc{mge} package\footnote{\url{http://www-astro.physics.ox.ac.uk/\~mxc/software/}} by \citet{Cappellari2002}. This is then used as an input for the \textsc{idl} routine \textsc{kinemetry}\footnote{\url{http://davor.krajnovic.org/idl/}} by \citet{Krajnovic2006} which finds the best-fitting ellipses at a range of evenly spaced semi-major axes. This is achieved by performing harmonic expansion of maps along ellipses with a given semi-major axis and, when used for even moments (e.g.\ surface brightness, velocity dispersion, h$_4$ etc.), minimizing the amplitude of the first and second harmonics. The results include the ellipticity, $\epsilon$ and position angle $PA_\text{phot}$ of the best-fitting ellipse for each semi-major axis. The fit is repeated for increasing semi-major axis until $<$75\% of the ellipse is not contained within the field of view.

	% In reality, the field of view does not always contain 1 $R_\mathrm{e}$. Where this is the case, we follow the method by \citet{Emsellem2007}, were $R_\mathrm{m}$ is redefined as $R_\mathrm{m} \equiv \sqrt{A_\mathrm{s}/\pi}$, where $A_\mathrm{s}$ is the area of the ellipse contained within the field of view. For a given galaxy, we fit ellipses as described above, up to $R_\mathrm{m} = R_\mathrm{max}$, where $A_\mathrm{s}$ reaches a maximum difference if 15\% to the area of the fitted ellipse, $A_\text{ellipse}$. The value $\epsilon_\mathrm{e}$, the ellipticity at 1 $R_\mathrm{e}$ or $R_\text{max}$, whichever is smallest, is given in Table \ref{tab:classify}.

	% Misalignment

	All other measurements (e.g. the specific angular momentum parapmeter $\lambda_\mathrm{R_e}$) and the classifications are made using the methods and critia described in the referenced literature above, with the results shown in Table \ref{tab:classify}.

>>>>

% mnras_template.tex
%
% LaTeX template for creating an MNRAS paper
%
% v3.0 released 14 May 2015
% (version numbers match those of mnras.cls)
%
% Copyright (C) Royal Astronomical Society 2015
% Authors:
% Keith T. Smith (Royal Astronomical Society)

% Change log
%
% v3.0 May 2015
%    Renamed to match the new package name
%    Version number matches mnras.cls
%    A few minor tweaks to wording
% v1.0 September 2013
%    Beta testing only - never publicly released
%    First version: a simple (ish) template for creating an MNRAS paper

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Basic setup. Most papers should leave these options alone.
\documentclass[a4paper,fleqn,usenatbib]{mnras}

% MNRAS is set in Times font. If you don't have this installed (most LaTeX
% installations will be fine) or prefer the old Computer Modern fonts, comment
% out the following line
\usepackage{newtxtext,newtxmath}
% Depending on your LaTeX fonts installation, you might get better results with one of these:
%\usepackage{mathptmx}
%\usepackage{txfonts}

% Use vector fonts, so it zooms properly in on-screen viewing software
% Don't change these lines unless you know what you are doing
\usepackage[T1]{fontenc}
\usepackage{ae,aecompl}

%%%%% AUTHORS - PLACE YOUR OWN PACKAGES HERE %%%%%

% Only include extra packages if you really need them. Common packages are:
\usepackage{graphicx}	% Including figure files
\usepackage{amsmath}	% Advanced maths commands
\usepackage{amssymb}	% Extra maths symbols

\usepackage[flushleft, referable]{threeparttablex} % Adding notes under tables
\usepackage{mhchem} 	% typeset chemistry symbols
\usepackage{multicol} 	% Multi-column entries in tables
% \usepackage{natbib} % references in text to look like MNRAS/ApJ/A&A
% \usepackage{multirow} % for multirow command
% \usepackage{array} % For wrapping text in cell in tables

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%%%%% AUTHORS - PLACE YOUR OWN COMMANDS HERE %%%%%

% Please keep new commands to a minimum, and use \newcommand not \def to avoid
% overwriting existing commands. Example:
%\newcommand{\pcm}{\,cm$^{-2}$}	% per cm-squared
\defcitealias{Thomas2010}{TMJ} % TMJ alias
% \newcolumntype{L}[1]{>{\raggedright\let\newline\\\arraybackslash\hspace{0pt}}m{#1}} % 
\newcommand{\bracket}[1]{[#1]} % to be able to use [] in arguments

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%%%%%%%%%%%%%%%%%%% TITLE PAGE %%%%%%%%%%%%%%%%%%%

% Title of the paper, and the short title which is used in the headers.
% Keep the title short and informative.
\title[An IFS study of Low-powered Radio Galaxies]{An IFS study of Low-powered Radio Galaxies}

% The list of authors, and the short list which is used in the headers.
% If you need two or more lines of authors, add an extra line using \newauthor
\author[J. Warren et al.]{
Joshua Warren,$^{1}$\thanks{Contact e-mail: \href{mailto:joshua.warren@physics.ox.ac.uk}{joshua.warren@physics.ox.ac.uk}}
Martin Bureau,$^{1}$
Bernd Hasemann,$^{2}$
Isabella Prandoni,$^{3}$ \newauthor
Francesco Santoro,$^{3}$
Robert Laing,$^{3}$
Paola Parma,$^{3}$
Hans de Ruiter$^{3}$
and \newauthor
Arturo Mignano$^{3}$
\\
$^{1}$Sub-department of Astrophysics, Department of Physics, University of Oxford, Denys Wilkinson Building, Keble Road, Oxford OX1 3RH, UK\\
$^{2}$European Southern Observatory, Karl-Schwarzschild-Str. 2, 85748 Garching b. München, Germany\\
$^{3}$INAF - Istituto di Radioastronomia, Via P. Gobetti 101, 40129 Bologna, Italy}

% These dates will be filled out by the publisher
\date{Accepted XXX. Received YYY; in original form ZZZ}

% Enter the current year, for the copyright statements etc.
\pubyear{2018}

% Don't change these lines
\begin{document}
\label{firstpage}
\pagerange{\pageref{firstpage}--\pageref{lastpage}}
\maketitle

% Abstract of the paper
\begin{abstract}
This is a simple template for authors to write new MNRAS papers.
The abstract should briefly describe the aims, methods, and main results of the paper.
It should be a single paragraph not more than 250 words (200 words for Letters).
No references should appear in the abstract.
\end{abstract}

% Select between one and six entries from the list of approved keywords.
% Don't make up new ones.
\begin{keywords}
% keyword1 -- keyword2 -- keyword3
\end{keywords}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%%%%%%%%%%%%%%%%% BODY OF PAPER %%%%%%%%%%%%%%%%%%

@@

	% One identifier of AGNs is a radio signature consistent with Synchrotron emission from the outflow i.e a radio galaxy (RG). These are typically categorized into one of two classes: Fanaroff-Riley (FR) I or FR II \citep{Fanaroff1974}. Of these we focus on the former since these are by far the most common mode in the local universe (possibly as far as $z \sim 1$ \citep{Rigby2008}), and so to discuss radio AGN feedback is to consider feedback from FR I sources \citep{DeYoung2010}. Indeed, while there is broad consensus \citep{Heckman1986, Baum1992} that the brightest RGs (mostly FR IIs) are caused when a massive galaxy merges with a gas rich galaxy (a wet merger) giving a plentiful fuel reservoir to the AGN \citep{Baum1992}, there is much more debate when it comes to low-powered ($P_\text{1.4 GHz} \lesssim 10^{24.5} \, \mathrm{W Hz^{-1}}$) RGs (mostly FR I). Suggestions fall into two categories: an extrapolation of radio-loud galaxies (i.e. a merger with either small gas reservoirs or low efficiency accretion onto the SMBH) or a highly efficient accretion of gas from secular origins (such as Bondi accretion of the hot X-ray component of the Inter-Stellar Medium (ISM) \citep{Allen2006} or from existing cold gas reservoirs \citep{Prandoni2010}). This project aims to add to this discussion using Integral Field Unit (IFU) observations in the visible band of nearby radio galaxies and comparing this with Atlas-3D sample \citep{Cappellari2011} as a control sample.

@@

	We refer to the combined Atlas$^\text{3D}$ and MASSIVE sample as the A+M sample.

@@

	\begin{table*}
		% \centering
	% \begin{threeparttable}
		\caption{Key sample characteristics of the Southern Sample galaxies. Col.\,1: host galaxy name. Col.\,2: radio source name from Parkes Southern Radio Source Catalogue. We hereafter refer to the last galaxy by its PKS name only. Col.\,3: redshift. Col.\,4: National Radio Astronomy Observatory (NRAO) Very Large Array (VLA) Sky Survey (NVSS) 1.4 GHz flux density \citep{Condon1998}. Col.\,5: Two Micron All Sky Survey (2MASS) $K$-band apparent magnitude (with errors of $\pm 0.025$ mag; \citealt{Skrutskie2006}). Col.\,6: dust morphologies from (a) \citet{Govoni2000}, (b) \citet{Lauer2005}, (c) \citet{Bettoni2001}, (d) \citet{Sandage1979}, (e) \citet{Colbert2001}.}
		\label{tab:sample}
		\begin{tabular}{l c c c c l}
			\hline
			\hline
			Host galaxy	& Radio source 	& Redshift	& $S_\text{1.4\,GHz}$	& $m_K$ & Dust morphology\\
						& (PKS) 		& 			& (mJy) 			& (mag)	&\\
			\hline 
			ESO 443-G024 & 1258-321 	& 0.01703	& $1387 \pm 45$		& 8.51 & no dust\tnote{a}	\\ 
			IC 1459 	& 2254-367 		& 0.00565 	& $1280 \pm 45$		& 6.81 & dust lane\tnote{b}	\\
			IC 1531 	& 0007-325 		& 0.02553 	& \leavevmode\phantom{0}$388 \pm 12$		& 9.55 & --					\\
			IC 4296		& 1333-\leavevmode\phantom{0}33 		& 0.01248 	& $1342 \pm 41$		& 7.50 & edge-on disc\tnote{b} \\
			NGC 612 	& 0131-\leavevmode\phantom{0}36 		& 0.02954 	& \leavevmode\phantom{0}$585 \pm 18$		& 9.58 & dust lane\tnote{c}	\\
			NGC 1316 	& 0320-\leavevmode\phantom{0}37 & 0.00591 	& \leavevmode\phantom{0}$255 \pm 10$		& 5.59 & dust patches\tnote{b} \\
			NGC 1399 	& 0336-\leavevmode\phantom{0}35 & 0.00472 	& \leavevmode\phantom{0}$209 \pm \leavevmode\phantom{0}7$	& 6.31 & no dust\tnote{b}	\\
			NGC 3100 	& 0958-314 		& 0.00879 	& \leavevmode\phantom{0}$530 \pm 16$		& 8.08 & dust lane\tnote{d}	\\
			NGC 3557 	& 1107-372 		& 0.01016 	& \leavevmode\phantom{0}$484 \pm 16$		& 7.20 & face-on disc\tnote{b}\\
			NGC 7075 	& 2128-388 		& 0.01819 	& \leavevmode\phantom{0}$837 \pm 28$		& 9.56 & --					\\
			--			& 0718-\leavevmode\phantom{0}34 		& 0.02897 	& $1119 \pm 41$		& 9.97 & dust patches\tnote{e} \\
			\hline
			\hline
		\end{tabular}
	% 	\begin{tablenotes}
	% 	\footnotesize
	% 	\note Col.\,1: host galaxy name. Col.\,2: radio source name from Parkes Southern Radio Source Catalogue. Col.\,3: redshift. Col.\,4: National Radio Astronomy Observatory (NRAO) Very Large Array (VLA) Sky Survey (NVSS) 1.4 GHz flux density \citep{Condon1998}. Col.\,5: Two Micron All Sky Survey (2MASS) $K$-band apparent magnitude (with errors of $\pm 0.025$ mag; \citealt{Skrutskie2006}). Col.\,6: dust morphologies from (a) \citet{Govoni2000}, (b) \citet{Lauer2005}, (c) \citet{Bettoni2001}, (d) \citet{Sandage1979}, (e) \citet{Colbert2001}. 
	% 	\item We hereafter refer to the last galaxy by its PKS name only.
	% 	\end{tablenotes}
	% \end{threeparttable}
	\end{table*}

@@

	Following this, we noted that the cubes where still not properly calibrated. Three main issues remain: the quadrants have different intensities, clearly showing uncorrected throughput differences; diagonal intensity stripes are present in the reconstructed images at all wavelengths; and spectral features are observed \citep{Jullo2008} that are visually similar to fringe patterns caused by interference within the CCD between incident light and light reflected from the interfaces between layers of the CCD materials. \citet{Lagerholm2012} present ad-hoc methods to correct for these issues, which we here adopt. These additional steps mean that the datacubes are not perfectly flux-calibrated, but all the corrections are multiplicative and thus will not effect equivalent width or line ratio measurements. From comparisons to the MUSE data (see Section \ref{subsec:MUSE}), we then estimate the flux calibration of the resulting datacubes.

	These method are not completely effective and some artefacts are still present in the data, however in most cases the data is of sufficient quality for our purposes. For the worst effected datacubes, we have archival observations (see Section \ref{subsec:MUSE}).

@@

		Finally, we trimmed all the MUSE cubes to the central $30\arcsec \times 30\arcsec$ ($150 \times 150$\,spaxels) only, to (a) avoid the regions used for the pseudo-sky spectrum and (b) reduce the computing resources required for spatial binning (see Section \ref{sec:analysis}). In any case, the bins would likely be so large in the outer parts as to be effectively useless.

\section{Data Analysis}
	\label{sec:analysis}
	From this point on, the VIMOS and MUSE datasets are treated almost identically, the only difference (other than the different spectral ranges and resolutions) being that the MUSE datacubes are spatially binned to a higher signal-to-noise ratio (S/N) using Voronoi binning\footnote{http://www-astro.physics.ox.ac.uk/~mxc/software/} \citep{Cappellari2003}. For our purposes, we define the `signal' and `noise' of each spaxel as the median value of its spectrum and noise spectrum, respectively. We require a S/N of 30 for all VIMOS datacubes and 50 for the IC 1459 and IC 4296 MUSE datacubes. The NGC 1316 and NGC 1399 MUSE datacubes were binned to a S/N of 50 for the analysis of the stellar kinematics and 100 for the analysis of the emission line kinematics and stellar populations.

	Next we implement a routine to find optimal initial guesses of the redshift and velocity dispersion for each galaxy, to be used when fitting individual bins, by means of iterative fits to the spatially collapsed (i.e. summed across both spatial dimensions of the datacube) spectrum. We use the penalized-fitting (\textsc{pPXF}) routine\footnote{http://www-astro.physics.ox.ac.uk/~mxc/software/} of \citet{Cappellari2004} and \citet{Cappellari2016a} with the Medium-resolution Issac Newton Telescope (INT) Library of Empirical Spectra (MILES) library \citep{Sanchez-Blazquez2006, Falcon-Barroso2011a} to find the best-fitting line-of-sight velocity distribution (LOSVD; as parametrised by the Gaussian parameters $v$, the mean velocity and $\sigma$, the velocity dispersion). The final mean velocity of a given galaxy, is used as its precise spectroscopic redshift and is given in Table \ref{tab:sample}. Beyond this point, each bin is analysed independently.

@@

		\begin{table}
	 		% \centering
	 	% \begin{threeparttable}
	 		\caption{Emission lines considered in the \textsc{pPXF} fits. Col\,1: Emission line name. Col\,2: Emission line rest-frame wavelength. Col\,3: Doublet rest-frame wavelength for forbidden lines. Col\,4: The fixed ratio of the amplitudes of the lines within a doublet. `Free' indicates the amplitudes of both doublet constituents are fit independently of each other.}
	 		\label{tab:EmissionLine}
	 		\begin{tabular}{l c c c}
	 		\hline
	 		\hline
	 		Emission & Rest-frame & Doublet rest-frame & Amplitude  \\
	 		Line & wavelength & wavelength & ratio \\
	 		 & (\AA) & (\AA) \\
	 		\hline
	 		\bracket{\ion{O}{ii}} 	& 3726.03 & 3728.82 & Free \\
	 		H\,$\delta$ 	& 4101.76 & -- & -- \\
	 		H\,$\gamma$ 	& 4340.47 & -- & -- \\
	 		H\,$\beta$ 		& 4861.33 & -- & -- \\
	 		\bracket{\ion{O}{iii}}	& 4958.92 & 5006.84 & 0.35 \\
	 		\bracket{\ion{N}{i}} 	& 5199.36 & 5201.86 & 0.65 \\
	 		\bracket{\ion{O}{i}} 	& 6300.30 & 6363.67 & 0.33 \\
	 		\bracket{\ion{N}{ii}} 	& 6548.03 & 6583.41 & 0.34 \\
	 		H\,$\alpha$ 	& 6562.30 & -- & -- \\
	 		\bracket{\ion{S}{ii}} 	& 6716.47 & 6730.85 & Free \\
	 		\hline
	 		\hline
	 		\end{tabular}
	 	% 	\begin{tablenotes}
	 	% 	\note Col\,1: Emission line name. Col\,2: Emission line rest-frame wavelength. Col\,3: Doublet rest-frame wavelength for forbidden lines. Col\,4: The fixed ratio of the amplitudes of the lines within a doublet. `Free' indicates the amplitudes of both doublet constituents are fit independently of each other. 
	 	% 	\end{tablenotes}
	 	% \end{threeparttable}
	 	\end{table}

@@

		\subsubsection{Correcting for Stellar Velocity Dispersion}
			We correct for the effect of the different velocity dispersions of the stars which varyingly spread absorption features such that differing fractions of the absorption is outside of the central bandpasses. To do this, we create a best-fitting spectrum (as in the previous step) which is \textit{not} convolved with the best-fitting LOSVD. A given index, $I$, is then measured for both this `unconvolved' spectrum ($I^\text{unc}$) and the convolved best-fitting spectrum ($I^\text{conv}$), and the ratio of these two indices is used as a multiplicative correction factor for the index measured ($I^\text{obs}$), such that the corrected index ($I^\text{corr}$) is given by
			\begin{equation}
				I^\text{corr} \equiv \frac{I^\text{unc}}{I^\text{conv}} I^\text{obs} \, .
			\end{equation}
			These corrected indices are those reported and discussed in the sections below.

@@

	\subsection{Other Parameters}
		\subsubsection{Ellipticity}
			In this paper, ellipticity is that of the best-fitting ellipse to the surface-brightness map with an mean radius $R_\text{m}$, of 1 effective radius $R_\text{e}$. % Firstly the centre of the galaxy is found as the luminosity weighted centre using the \textsc{python} routine \textsc{find\_galaxy}, which is part of the \textsc{mge} package\footnote{http://www-astro.physics.ox.ac.uk/\~mxc/software/} by \citet{Cappellari2002}. 
			as found by the \textsc{idl} routine \textsc{kinemetry}\footnote{http://davor.krajnovic.org/idl/} by \citet{Krajnovic2006} which finds the best-fitting ellipses at a range of evenly spaced semi-major axes. %This is achieved by performing harmonic expansion of maps along ellipses with a given semi-major axis and, when used for even moments (e.g.\ surface brightness, velocity dispersion, h$_4$ etc.), minimizing the amplitude of the first and second harmonics. 
			The results include the ellipticity, $\epsilon$ and position angle $PA_\text{phot}$ of the best-fitting ellipse for each semi-major axis. The fit is repeated for increasing semi-major axis until $<$75\% of the ellipse is not contained within the field of view.

			In reality, the field of view does not always contain 1 $R_\text{e}$. Where this is the case, we follow the method by \citet{Emsellem2007}, where $R_\text{m}$ is redefined as $R_\text{m} \equiv \sqrt{A_\text{s}/\pi}$, where $A_\text{s}$ is the area of the ellipse contained within the field of view. For a given galaxy, we fit ellipses as described above, up to $R_\text{m} = R_\text{max}$, where $A_\text{s}$ reaches a maximum difference if 15\% to the area of the fitted ellipse, $A_\text{ellipse}$. The value $\epsilon_\text{e}$, the ellipticity at 1 $R_\text{e}$ or $R_\text{max}$, whichever is smallest, is given in Col.\,3 of Table \ref{tab:classify}.

		\subsubsection{Kinematic Position Angle}
			The kinematic position angle, $PA_\text{kin}$, is defined as the angle of the axis perpendicular to the apparent angular momentum vector westwards from North. A global value of $PA_\text{kin}$ is found using the \textsc{python} routine \textsc{fit\_kinematic\_pa}\footnote{http://www-astro.physics.ox.ac.uk/\~mxc/software/\#pa\_kin} which finds $PA_\text{kin}$ of the symmetrised mean velocity map, as described in appendix C of \citet{Krajnovic2006}. %This routine finds a symmetric (about $PA_\text{kin}$) velocity field, by replacing the mean velocity, $V$, in each bin with
			% \begin{equation}
			% 	V'(x, y) = \frac{V(x,y) + V(x, -y) - V(-x,y) - V(-x,-y))}{4} \,,
			% \end{equation}
			% where $x$ and $y$ are the centroid coordinates of a given bin, with the origin at the centre of the galaxy and the x axis aligned along $PA_\text{kin}$. Linear interpolation is used where necessary.

			Col.\,4 in Table \ref{tab:classify} lists the misalignments between the photometric and kinematic position angles, $\Gamma_\text{kin} \equiv \arcsin(\sin[PA_\text{phot} - PA_\text{kin}])$.

		\subsubsection{Specific Angular Momentum Parameter, $\lambda_\mathrm{R_e}$}
			We also make use of the Atlas$^\text{3D}$ specific angular momentum parameter, $\lambda_\text{R}$ \citep{Emsellem2007} evaluated at 1 $R_\text{e}$, where 
			\begin{equation}
				\lambda_\mathrm{R_e} \equiv \frac{\sum_{i=1}^{N} F_i R_i |V_i|}{\sum_{i=1}^{N} F_i R_i \sqrt{V_i^2 + \sigma_i^2}}
			\end{equation}
			where $F_i$ is the flux of the $i^\text{th}$ bin, $R_i$ its distance from the centre and $V_i$ and $\sigma_i$ its mean stellar velocity and velocity dispersion, respectively. The sum is computed over all $N$ bins with a radius $R_\text{e}$.
